\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2021-02-24 popl-2019-journal-v/paper.tex
Add some very recent additional references.

Local capabilities can be used to ensure well-bracketed control-flow and local-state encapsulation as demonstrated by \citet{skorstengaard_reasoning_2017}.
Recently, \citet{tsampas_2019} demonstrated that an extension of local capabilities with multiple linearly ordered colours can be used to enforce the life time of stack references.
Specifically, a stack reference should not be able to outlive the stack frame it points to.
If \stktokens{} was extended with stack references, then it would also enforce reference life times.
Specifically in order to return from a call, we must use the return token, i.e.\ the stack.
The stack is linear, so if there are references to it, aside from the stack capability itself, then we cannot have a complete return token.
This means that we have to splice all the stack references together with the stack capability to complete the return token in order to return.
\citet{tsampas_2019} allow (almost) normal references that can be stored in multiple places at the same time.
This means that their approach is closer to C than \stktokens{}.
As explained in Section~\ref{sec:introduction}, these approaches have the downside that they require stack clearing (including unused parts) on boundary crossings.

>>>>

Local capabilities can be used to ensure well-bracketed control-flow and local-state encapsulation as demonstrated by \citet{skorstengaard_reasoning_2017,skorstengaard_reasoning_2019}.
Recently, \citet{tsampas_2019} demonstrated that an extension of local capabilities with multiple linearly ordered colours can be used to enforce the life time of stack references.
Specifically, a stack reference should not be able to outlive the stack frame it points to.
If \stktokens{} was extended with stack references, then it would also enforce reference life times.
Specifically in order to return from a call, we must use the return token, i.e.\ the stack.
The stack is linear, so if there are references to it, aside from the stack capability itself, then we cannot have a complete return token.
This means that we have to splice all the stack references together with the stack capability to complete the return token in order to return.
\citet{tsampas_2019} allow (almost) normal references that can be stored in multiple places at the same time.
This means that their approach is closer to C than \stktokens{}.
As explained in Section~\ref{sec:introduction}, these approaches have the downside that they require stack clearing (including unused parts) on boundary crossings.
Very recently, \citet{georges_efficient_2021} have proposed a version of \citeauthor{skorstengaard_reasoning_2017}'s calling convention which succesfully avoids the need for stack clearing by relying on a newly proposed form of capabilities called uninitialized capabilities and they have proven soundness of the approach using Coq and the Iris program logic \citep{jung_iris_2018}.
